---
title: "HM 1 - Matrix Algebra"
author: "PSY 533"
date: "Wednesday, January 14, 2015"
output: pdf_document
---


**DUE**: January 23, before midnight  

**INSTRUCTIONS**: Submit work as an R file emailed to piccinin@uvic.ca and andkov@uvic.ca

**NAMING**: Please name your file: "PSY-533-HM1-Lastname-Firstname.R"


### 1.  Demonstrations

With two randomly generated  matrices of the order (5,1), demonstrate the work of:   

a) Associative Law of matrix addition  
```{r}

```

b) Distributive Law of matrix addition  
```{r}

```

Using the matrices from **3.Computations** of this HM demonstrate:

c)  Associative rule of matrix multiplication

```{r}

```

d)  Distributive rule of matrix multiplication
```{r}

```

e)  that matrix multiplication is not commutative
```{r}

```


### 2. Word problem
Given the data vector
```
4, 7, 2, 5, 8
```
transform the standardized scores so that  its variance quadruplesand and the new mean becomes equal to the value of raw scores's median. Round to remove decimals. 


```{r, eval=F, echo=F, results='hide'}
X <- c(4, 7, 2, 5, 8)
X

dX <- X - mean(X)
dX

zX <- dX/sd(X)
zX

var(zX)
mean(zX)


ltX <- zX * 2 + median(X)
ltX

round((ltX))

```

### 3.  Computations
Given the matrices
$$
\begin{array}{*{20}{c}}
{{\bf{A}} = \left[ {\begin{array}{*{20}{c}}
1&3&4\\
5&0&8\\
3&2&9
\end{array}} \right]}&{}&{{\bf{B}} = \left[ {\begin{array}{*{20}{c}}
1&3&{13}\\
2&3&1\\
1&3&8
\end{array}} \right]}&{}&{{\bf{C}} = \left[ {\begin{array}{*{20}{c}}
6&7&4\\
8&6&2\\
{19}&{11}&8
\end{array}} \right]}
\end{array}
$$



Compute the following:

a) ${\bf{A + B}}\\$ 

b) ${\bf{CC'}}\\$

c) ${\bf{A - C}}\\$

d) $Tr({\bf{AA}}){\bf{'}}\\$

e) $Tr({\bf{A'C}})$





### 4. Are you smarter than a fifth-grader?
Solve with matrix algebra in R:
$$ 
\begin{array}{l}
2x + 2y = 3\\
x - 4y =  - 1
\end{array}
$$
